\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{biblatex}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Dmitry Doronin}

\address{New York, NY}
\address{(347)224-9982 \\ \href{mailto:doronindm@gmail.com}{doronindm@gmail.com}}

\begin{document}


%----------------------------------------------------------------------------------------
%	Primary skills
%----------------------------------------------------------------------------------------

\begin{rSection}{}
13 years of professional software development as a back-end, data and front-end engineer.

• front-end: React, RxJS, Vue, Backbone, Yew (personal projects);

• back-end: Elixir, Scala, Nodejs, .Net, Rust (personal projects);

• big data: Spark, Hadoop;

• databases: MongoDB, MsSQL, PostgreSQL.

Interested in distributed systems, algorithms, ML, and programming languages.

Author of JavaScript Reactive Hooks library: 
https://github.com/reonomy/reactive-hooks

BLog: 
https://medium.com/@dmitrydoronin

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Senior Software Engineer, Dataminr, \url{https://www.dataminr.com}}{Nov 2021 - Jan 2023}{}{}
\item Led design and development of a distributed highly scalable web service in Elixir. This service aggregates data from all Dataminr microservices and operates as a frontier for all Front-Ends (web, mobile, email, integrations such as slack, etc.)

Tech stack: Elixir, Phoenix, Absinthe, GraphQL, Backstage, AWS, ECS.
\end{rSubsection}

\begin{rSubsection}{Founding Engineer, Smartrr, \url{https://smartrr.com}}{Dec 2020 - Jun 2021}{}{}
\item Designed the back-end architecture and implemented a billing engine and advanced subscriptions features such as add-ons, skips, gifts, anchor dates, etc.

Tech stack: Node, TypeScript, GraphQL, React, PostgreSQL, Kubernetes, GCP.
\end{rSubsection}

\begin{rSubsection}{Staff Software Engineer, Reonomy, \url{http://reonomy.com}}{Feb 2019 - Dec 2020}{Roles: Data Engineer, Front-End Tech Lead, Back-End Engineer}{}
\item Featured in "The Road to React..." \url{https://www.reonomy.com/blog/post/reactive-hooks}
\item Led \href{https://www.reonomy.com/blog/post/reonomy-launches-ownership-portfolio-beta}{Ownership Portfolios} development from the ground up.

Tech stack: Scala, Spark, GraphX, Python, React, TypeScript, RxJS, Airflow, ES, PostgreSQL.
\end{rSubsection}

\begin{rSubsection}{Lead Software Engineer, EPAM Systems, \url{https://www.epam.com}}{Nov 2018 - Feb 2019}{Contractor at Scripps Networks Interactive / Front-End Tech Lead}{}
\item Led web application front-end development for Scripps Food Network.
\item Automated CI/CD front-end pipeline based on Vue CLI 3 Plugins.

Tech stack: JavaScript, Vue, NodeJS, Ruby, Java, AWS.
\end{rSubsection}

\begin{rSubsection}{Lead Software Engineer, EPAM Systems, \url{https://www.epam.com}}{Jan 2016 - Oct 2018}{Contractor at Goldman Sachs / Full-Stack Developer}{}
\item[] \textbf{May 2018 - Oct 2018, Marquee, Trading and risk-management platform.}
\item Development of the FX order execution platform. \url{https://marquee.gs.com/solutions/trader}

\item[] \textbf{Jan 2016 - Apr 2018, SIMON, Structured products investment platform.}
\item Architecture design and development of a real-time investment platform. \url{https://www.simon.io}

Tech stack: Scala, Akka, WebSockets, MongoDB, BackboneJS, React, MobX, TypeScript, Protractor.
\end{rSubsection}


\begin{rSubsection}{Lead Software Engineer, EPAM Systems, \url{https://www.epam.com}}{Aug 2014 - Dec 2015}{Contractor at Thomson Reuters / Team Lead, Key Front-End Developer}{}
\item Led a team of 4 software developers and 2 QAs.
\item Developed Eikon Apps: Portfolio Dashboard, Fundamentals, Aggregate Report and Grid Report.
\item[] \url{https://eikon.thomsonreuters.com/}
\item Key contributor to the proprietary virtualized grid library used across TR products.
\item Performance tuning for intensive calculations on FE with Web Workers.
\item Responsible for sprint planning, tasks assignments, progress tracking and delivery.

Tech stack: JavaScript, AngularJS, LESS, NodeJS, Gulp, Bower, ASP .NET Web API 2, Silverlight.
\end{rSubsection}

\begin{rSubsection}{Senior Software Engineer, EPAM Systems, \url{https://www.epam.com}}{Sep 2011 - Jul 2014}{Contractor at Telligent / Full-Stack Key Developer}{}
\item Core features development for Telligent Community Server. \url{https://www.telligent.com}
\item Addons development for Ms SharePoint integration via Telligent extensions and Scripted Widgets.

Tech stack:  ASP .Net, WinForms, WCF, NUnit, Windows Services, MsSQL, proprietary Telligent Scripted API and Scripted Widgets, ES5, JQuery, HTML5, CSS3, LESS.
\end{rSubsection}


\begin{rSubsection}{Software Engineer, EPAM Systems, \url{https://www.epam.com}}{Jun 2011 - Aug 2011}{Full-Stack Developer}{}
\item Internal proprietary services development.

Tech stack: C\#, .Net WPF, ASP.Net, WCF, JavaScript, jQuery, MsSQL.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}{Saratov State University named after N.G.Chernyshevsky, \url{https://www.sgu.ru/en}}{}{}{}

      2010 | 2013 PhD, All But Dissertation.

      2005 | 2010 Master's degree in Radiophysics and Electronics.


      Author of 14 publications in electrodynamics, mathematics and computer science:
      \item[] \url{https://www.researchgate.net/scientific-contributions/2013742207_D_M_Doronin}
      \item[] \url{https://elibrary.ru/item.asp?id=15117920}

\bigskip
\renewcommand{\section}[2]{\textbf{SELECTED PUBLICATIONS}}
\begin{thebibliography}{}

    \bibitem{} 
    A.N.Savin, I.A.Nakrap, D.M.Doronin
    \textit{The equivalent circuit parameters calculation of a coupled cavity chain using electrodynamic characteristics}
    IEEE, 2010.

    \url{https://ieeexplore.ieee.org/document/5632593}

    \bibitem{} 
    A.N.Savin, I.A.Nakrap, D.M.Doronin
    \textit{The high-order optimal design of experiment development on the base of regular simplex for the slow-wave structures characteristics modeling}
    IEEE, 2010.

    \url{https://ieeexplore.ieee.org/document/5632591}


    \bibitem{latexcompanion} 
    M.V.Davidovich, A.N.Savin, D.M.Doronin
    \textit{Electromagnetic properties of metallic photonic crystals}
    IEEE, 2010.

    \url{https://ieeexplore.ieee.org/document/5632577}
\end{thebibliography}

\end{rSubsection}
\end{rSection}


\end{document}
